Enzo: An Adaptive Mesh Refinement Code for Astrophysics

### 2013-10-26 refreport/response.tex

Regarding test problems, the referee's comment is:

\begin{verbatim}
However, the paper is let down due to the lack of tests presented for
many of the algorithms presented in the paper. In particular, the only
test presented for the MHD algorithm is the Orszag-Tang vortex test,
which 'does not seem to be extremely discriminating for MHD
algorithms' (Stone et al., 2008). In addition, results from some
tests, such as the photo-evaporation test, do not seem to be properly
compared to prior results in the literature (e.g. Jiang et
al. 2012). Finally, no tests appear to be presented for some tests
entirely, e.g. the Chemistry algorithms presented in Section 6.1.
\end{verbatim}

We have modified the test problem section as follows:

\begin{itemize}
\item We have added a section (11.2.10) showing how both \enzo\ MHD
  algorithms perform on the standard Brio \& Wu shock tube test
  problem, which is a standard test of MHD solvers.  Both \enzo\ MHD
  algorithms match the reference solution to high precision.  We retain the
  Orszag-Tang Vortex test as we fell that it is interesting to the
  intended audience.

\item We have added a test of the non-equilibrium primordial chemistry code that
  tests the ionization balance in ionized gas as compared to an
  analytical solution (Section 11.2.13).  As can be seen, \enzo's
  non-equilibrium chemistry solver  reproduces the analytical solution perfectly.

\item The ``Photo-evaporation of a dense clump'' test problem (Section
  11.2.14) has been expanded to include a new figure (Fig. 18) that
  contains much more detail about the evolution of the test problem,
  and comparison to prior results, including the MORAY method paper
  \citep{Wise11_Moray} and the Cosmological Radiative Transfer
  Comparison Project paper \citep{IlievEtAl2009}.

\end{itemize}

We also note that many of the fundamental \enzo\ algorithms are
extensively tested in separate method papers that focus on a single
algorithm/physics package, and a single test problem or small number
of test problems are included in the full \enzo\ method paper as a
demonstration that the algorithms behave sensibly.  In the paper's
section or subsection
describing these algorithm, we cite the full method paper for the
appropriate algorithm and the direct the reader to it for more
information.  These additional algorithm method papers include ones
for both flavors of MHD contained in \enzo\ \citep{Wang:2009a,
Collins10}, the ray-tracing code \citep{Wise11_Moray}, and the
flux-limited diffusion \citep{ReynoldsHayesPaschosNorman2009}.

@@

Finally, we would like to address the referee's feedback regarding the
paper's length and current organization.  The referee's comment is:

\begin{verbatim} 
Given the paper's length as it currently stands, it seems appropriate
to split the paper into two. One paper should document the basic
algorithms (e.g. AMR, hydro, MHD and gravity implementations) along
with an appropriate range of tests based on standard tests from the
literature. The second paper should document the microphysics options
(chemistry, radiation, thermal conductivity, etc.).
\end{verbatim}

We respectfully disagree with the referee regarding this point --
splitting the paper in two does not make sense, will not shorten the
overall page count, and will not improve the clarity of presentation. One of the strengths
of the \enzo\ code is the breadth of physics packages that are
available in the publicly-available version -- unlike, for example,
Gadget and Gadget-2 \citep{2001NewA....6...79S, 2005MNRAS.364.1105S},
where the only physics packages that are publicly available are dark
matter and adiabatic hydrodynamics.  Given this, it is logical that
the totality of the code's capabilities be documented in a single
place, for reference by future generations of computational scientists.

Regarding the paper's length, we argue that it is not excessively long
given the topics it covers, and thus does not need to be split into
multiple parts.  At present, the \enzo\ method paper is 62 pages long
in ApJ format.
For comparison:

@@

We further note that splitting the paper up into two separate pieces
provides structural challenges, and will serve to increase the total
page count.  Structurally, Section 2 (the ``overview'' section) would
need to be split into two pieces, and the component that discusses the
microphysics will be somewhat confusing on its own, as these modules
act as sink and source terms for the fluid equations that would in
principle be described in a separate paper.  It's not clear where
Section 10 (``Analysis''), Section 12 (``Parallel strategy and
performance''), and Section 13 (``Code development methodology'')
would logically go -- some of these sections apply to all physics
packages in the code (e.g., Section 12), and others to none in
particular (e.g., Section 13).  Similarly, Section 11.1 (``Verifying
and validating the Enzo code'') describes the \enzo\ test suite, which
is used for all aspects of code testing (including both the
fluid/gravity/AMR algorithms \textit{and} the microphysics), and also
for code comparisons that test many different aspects of the code,
often in combination.  In order for these sections to make sense, and
to address test problems that are split between two papers, several of
these sections would need to be either duplicated or require an
extensive amount of cross-referencing between papers Furthermore,
separate introductions, discussions, and conclusions will by necessity
be mutually referential and, in some sense, duplicates of each other.
Together, this will not serve to either decrease page count or
increase clarity for the reader.

\section{Additional changes}

In addition to directly addressing concerns expressed by the referee,
we have fixed additional typos in the paper.  These include:

\begin{enumerate}
\item  We have corrected a typo in the equation describing the Jeans
  length refinement criterion (Equation 29).

\item We have corrected a typo in Table 4, where two photoionization
  rates were accidentally switched in the submitted version.

\item We have added missing acknowledgments.

\end{enumerate}

### 2013-10-28 tests-vandv.tex
updated the paper w/enzo 2.3 changeset hash

After the test problems are selected by the test runner script, they
are run in succession using either the \enzo\ executable contained
within that distribution or an external executable built from another
\enzo\ version and specified by the user.  This allows for any version
of the code to be tested with an identical set of test problems.
After running the test problem simulations, the test runner then
performs a series of basic analysis tasks using the \texttt{yt}
analysis toolkit \citep{2011ApJS..192....9T, 2011arXiv1112.4482T}.
The default analysis performed on all test problems includes
calculation of various statistics (such as extrema, mean, and
variance) on the fields present in the output data.  Custom analysis
provided by scripts that accompany the test problem parameter files is
run for special cases, such as when an analytical solution exists that
can be compared against the simulation data.  After the analysis is
performed, the results are compared against a set of gold standard
results that are maintained on a website and downloaded on the fly by
the test runner script.  Alternately, results from any version of
\enzo\ can be stored locally and compared to any other version of the
code.  In Section~\ref{sec.tests.problems}, we describe some of the
key test problems that are used to verify proper behavior.  All of
these test problems, as well as the scripts to generate the figures
from them, are available at
\url{http://bitbucket.org/enzo/enzo-method-paper}, the Bitbucket
repository for the \enzo\ method paper.  The \texttt{test\_problems}
subdirectory in this repository contains all of the files necessary to
regenerate all of the figures in Section~\ref{sec.tests.problems}.  We
note for completeness that the figures in
Section~\ref{sec.tests.problems} were generated using \texttt{yt}
version 2.5.3 and the \url{https://bitbucket.org/enzo/enzo-dev}
repository of \enzo\ with changeset \texttt{5d8c412}, which
corresponds to \enzo\ 2.3.

>>>>

After the test problems are selected by the test runner script, they
are run in succession using either the \enzo\ executable contained
within that distribution or an external executable built from another
\enzo\ version and specified by the user.  This allows for any version
of the code to be tested with an identical set of test problems.
After running the test problem simulations, the test runner then
performs a series of basic analysis tasks using the \texttt{yt}
analysis toolkit \citep{2011ApJS..192....9T, 2011arXiv1112.4482T}.
The default analysis performed on all test problems includes
calculation of various statistics (such as extrema, mean, and
variance) on the fields present in the output data.  Custom analysis
provided by scripts that accompany the test problem parameter files is
run for special cases, such as when an analytical solution exists that
can be compared against the simulation data.  After the analysis is
performed, the results are compared against a set of gold standard
results that are maintained on a website and downloaded on the fly by
the test runner script.  Alternately, results from any version of
\enzo\ can be stored locally and compared to any other version of the
code.  In Section~\ref{sec.tests.problems}, we describe some of the
key test problems that are used to verify proper behavior.  All of
these test problems, as well as the scripts to generate the figures
from them, are available at
\url{http://bitbucket.org/enzo/enzo-method-paper}, the Bitbucket
repository for the \enzo\ method paper.  The \texttt{test\_problems}
subdirectory in this repository contains all of the files necessary to
regenerate all of the figures in Section~\ref{sec.tests.problems}.  We
note for completeness that the figures in
Section~\ref{sec.tests.problems} were generated using \texttt{yt}
version 2.5.3 and the \url{https://bitbucket.org/enzo/enzo-dev}
repository of \enzo\ with changeset \texttt{bad70b86fcd6}, which
corresponds to the \enzo\ 2.3 code release.
